---
output: github_document
---

# imlplots: interpretable machine learning plots
 `imlplots ` is an R package that provide an interactive Shiny dashboard for three kinds of Interpretable Machine Learning (IML) plots
 
* Partial Dependence Plots (PDP)
* Individual Conditional Expectation (ICE) plots
* Accumulated Local Effect (ALE) plots



```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
set.seed(42)
```

# Installation 
The package can be installed directly from github with devtools:
```{r, results = 'hide', eval = FALSE}
# install.packages("devtools")
devtools::install_github('riebetob/imlplots')
library(imlplots)
```


# Quickstart
You can fit classification and regression problems from the `mlr` package and analyse possible interaction effects in the Shiny dasbhoard.

For quickstart we take the popular Boston Housing data, where we want to predict the median housing price in Boston.
```{r}
library(MASS)
data(Boston)
```

For using `imlplots` Shiny dashboard, three input arguments need to be specified

* `data` - the input data
* `task`- the learning task
* `models` - one or several trained models

We create a regression task with `medv` as target variable.
The task structure is determined by `mlr` package.
```{r}
library(mlr)
boston.task = makeRegrTask(data = Boston, target = "medv")
```

The `imlplots` dashboard allows the comparison of multiple learning algorithms, therefore we fit two different models - first a random forest and second a SVM.
```{r}
rf.mod = train("regr.randomForest", boston.task)
svm.mod = train("regr.ksvm", boston.task)
```

The input for the Shiny app is a list of learners.
```{r}
mod.list = list(rf.mod, svm.mod)
```

Now the Shiny app can be used.
```{r, eval=FALSE}
imlplots(data = Boston, task = boston.task, models = mod.list)
```

# References

* [PDP and ICE plots](https://arxiv.org/pdf/1309.6392.pdf)
* [mmpf R package](https://github.com/zmjones/mmpf)
* [ALE plots](https://arxiv.org/abs/1612.08468)
* [ALE R package](https://cran.r-project.org/web/packages/ALEPlot/index.html)



